\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-11-12 paper.tex

%In this section, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors. 
%This is achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
%This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.

We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions. We denote as $q_{ij}\in\real{m}$ the position of agent $i$ at the discrete-time index $j$, with $m$ representing the dimension of the state space. For a total of $n_p$ robots, and a task time horizon of $T$, a total of $n_p$ trajectories can be represented as an aggregated vector $\vq\in \real{n m T}$. 
The overall goal is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraintsand the security constraints (co-observation schedule, reachability analysis). Formally:
\begin{equation}\label{eq:general-problem}
	\begin{split}
		\min/\max & \quad \varPhi(\vq)\\
		\textrm{subject to} &\quad \vq \in \Omega.
	\end{split}
\end{equation}

>>>>

In this section, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors. 
This is achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
\begin{definition}\label{def:secured-plan}
  A multi-robot trajectory plan is secure again plan-deviation attacks if it ensures that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots. 
\end{definition}

%This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.

\rtron{Clarify when we use bold symbols. Make sure this is used consistently.}
We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions. We denote as $q_{ij}\in\real{m}$ the position of agent $i$ at the discrete-time index $j$, with $m$ representing the dimension of the state space. For a total of $n_p$ robots, and a task time horizon of $T$, a total of $n_p$ trajectories can be represented as an aggregated vector $\vq\in \real{n m T}$. 
The overall goal is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraintsand the security constraints (co-observation schedule, reachability analysis). Formally:
\begin{equation}\label{eq:general-problem}
	\begin{split}
		\min/\max & \quad \varPhi(\vq)\\
		\textrm{subject to} &\quad \vq \in \Omega.
	\end{split}
\end{equation}
